%%%%
% MTecknology's Resume
%%%%
% Author: Michael Lustfield
% License: CC-BY-4
% - https://creativecommons.org/licenses/by/4.0/legalcode.txt
%%%%

\documentclass[letterpaper,10pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%
%% BEGIN_FILE: mteck.sty
%% NOTE: Everything between here and END_FILE can
%% be relocated to "mteck.sty" and then included with:
%\usepackage{mteck}

% Dependencies
% NOTE: Some packages (lastpage, hyperref) require second build!
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{bookmark}
\usepackage{lastpage}

% Sans-Serif
%\usepackage[sfdefault]{FiraSans}
%\usepackage[sfdefault]{roboto}
%\usepackage[sfdefault]{noto-sans}
%\usepackage[default]{sourcesanspro}

% Serif
\usepackage{CormorantGaramond}
\usepackage{charter}

% Colors
% Use with \color{Name}
% Can wrap entire heading with {\color{accent} [...] }
\usepackage{xcolor}
\definecolor{accentTitle}{HTML}{0e6e55}
\definecolor{accentText}{HTML}{0e6e55}
\definecolor{accentLine}{HTML}{a16f0b}

% Misc. Options
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\urlstyle{same}

% Adjust Margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.4in}

\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\setlength{\tabcolsep}{0pt}
\setlength{\footskip}{3.7pt}
\raggedbottom
\raggedright

% ATS Readability
\input{glyphtounicode}
\pdfgentounicode=1

%-----------------%
% Custom Commands %
%-----------------%

% Centered title along with subtitle between HR
% Usage: \documentTitle{Name}{Details}
\newcommand{\documentTitle}[2]{
  \begin{center}
    {\Huge\color{accentTitle} #1}
    \vspace{10pt}
    {\color{accentLine} \hrule}
    \vspace{2pt}
    %{\footnotesize\color{accentTitle} #2}
    \footnotesize{#2}
    \vspace{2pt}
    {\color{accentLine} \hrule}
  \end{center}
}

% Create a footer with correct padding
% Usage: \documentFooter{\thepage of X}
\newcommand{\documentFooter}[1]{
  \setlength{\footskip}{10.25pt}
  \fancyfoot[C]{\footnotesize #1}
}

% Simple wrapper to set up page numbering
% Usage: \numberedPages
% WARNING: Must run pdflatex twice!
\newcommand{\numberedPages}{
  \documentFooter{\thepage/\pageref{LastPage}}
}

% Section heading with horizontal rule
% Usage: \section{Title}
\titleformat{\section}{
  \vspace{-5pt}
  \color{accentText}
  \raggedright\large\bfseries
}{}{0em}{}[\color{accentLine}\titlerule]

% Section heading with separator and content on same line
% Usage: \tinysection{Title}
\newcommand{\tinysection}[1]{
  \phantomsection
  \addcontentsline{toc}{section}{#1}
  {\large{\bfseries\color{accentText}#1} {\color{accentLine} |}}
}

% Indented line with arguments left/right aligned in document
% Usage: \heading{Left}{Right}
\newcommand{\heading}[2]{
  \hspace{10pt}#1\hfill#2\\
}

% Adds \textbf to \heading
\newcommand{\headingBf}[2]{
  \heading{\textbf{#1}}{\textbf{#2}}
}

% Adds \textit to \heading
\newcommand{\headingIt}[2]{
  \heading{\textit{#1}}{\textit{#2}}
}

% Template for itemized lists
% Usage: \begin{resume_list} [items] \end{resume_list}
\newenvironment{resume_list}{
  \vspace{-7pt}
  \begin{itemize}[itemsep=-2px, parsep=1pt, leftmargin=30pt]
}{
  \end{itemize}
  %\vspace{-2pt}
}

% Formats an item to use as an itemized title
% Usage: \itemTitle{Title}
\newcommand{\itemTitle}[1]{
  \item[] \underline{#1}\vspace{4pt}
}

% Bullets used in itemized lists
\renewcommand\labelitemi{--}

%% END_FILE: mteck.sty
%%%%%%%%%%%%%%%%%%%%%%


%===================%
% Amit's Resume %
%===================%

%\numberedPages % NOTE: lastpage requires a second build
%\documentFooter{\thepage of 2} % Does similar without using lastpage
\begin{document}

  %---------%
  % Heading %
  %---------%

  \documentTitle{Amit Kumar}{
    % Web Version
    %\raisebox{-0.05\height} \faPhone\ [redacted - web copy] ~
    %\raisebox{-0.15\height} \faEnvelope\ [redacted - web copy] ~
    %%
    \href{tel:1234567890}{
      \raisebox{-0.05\height} \faPhone\ +91 } ~ | ~
    \href{mailto:amitkr20020405@gmail.com}{
      \raisebox{-0.15\height} \faEnvelope\ amitkr20020405@gmail.com} ~ | ~
\href{https://www.linkedin.com/in/amit-kumar-278563194/}{
  \raisebox{-0.15\height} \faLinkedin\ Amit} ~ | ~
    \href{https://github.com/Amit-syntax/}{
      \raisebox{-0.15\height} \faGithub\ github.com/Amit-syntax}
  }

  %---------%
  % Summary %
  %---------%
\tinysection{Professional Summary}
A Backend Engineer over 5+ years of experience, skilled in Go, Python, JavaScript, TypeScript, and DevOps practices.
Expertise in building scalable cloud solutions, automating infrastructure, and optimizing AI-driven systems. Proven track
record in delivering high-performance, resource-efficient applications
  %--------%
  % Skills %
  %--------%

  \section{Skills}

  \begin{flushleft}
    \begin{itemize}[itemsep=-2px, parsep=1pt, leftmargin=75pt]
      \item[\textbf{Languages}] Go, Python, JavaScript, TypeScript, Bash.
      \item[\textbf{Devops}] Kubernetes, Docker, Grafana, Prometheus, Ansible.
      \item[\textbf{Databases}] MongoDB, MySQL, PostgreSQL, Pinecone, chromaDB.
      \item[\textbf{Cloud}] AWS (EC2, S3, SES, IAM, Cloudformation, Route53)
      \item[\textbf{Frameworks}] Djanog, FastAPI, Express.js, Ray.io
      \item[\textbf{Libs}] Panadas, Numpy, matplotlib.
      \item[\textbf{Testing}] Pytest, Vitest
      \item[\textbf{Others}]  Linux, REST, Nginx, Apache2, Apache Kafka
    \end{itemize}
  \end{flushleft}

  %------------%
  % Experience %
  %------------%

  \section{Experience(5+yrs)}

  \headingBf{Codewave}{Aug 2022-Present}
  \headingIt{Backend Engineer}{SDE}

  \begin{resume_list}

\itemTitle{Client: Hosted.ai}
\item Developed scalable Go backend solution for an AI infrastructure platform optimizing GPU utilization and enabling \textbf{GPU-as-a-Service} (GPUaaS) for enterprises and service providers.
\item Automated GPUaaS deployment workflows using Ansible for infrastructure provisioning and configuration management.
\item Integrated Kubernetes with \textbf{Ray.io} to efficiently manage distributed AI workloads.
\item Configured the Prometheus stack for service discovery and real-time monitoring.
\item Set up Grafana dashboards for comprehensive system performance and resource usage visualization.
\item \textbf{Technologies Used:} Go, Python, Ansible, Kubernetes, Ray.io, Prometheus, Grafana, Docker, MySQL, Bash.
\vspace{3pt}

\itemTitle{Glue - (B2B SaaS)}
\item the platform glue is a B2B SaaS product for self management
\item \textbf{Technologies Used:} Typescript, NodeJs, RESTfull API, Docker, MongoDB.
\vspace{3pt}


\end{resume_list}

\headingBf{Fyers (outsourced by codewave)}
\headingIt{Backend Engineer}

  \begin{resume_list}
  \itemTitle{Myaccount Platform(Maintenance) }
  \item Trading accounts platform rewritting in golang.
  \item Handling automation of data in python.
  \item Calculations of multiple metrics(holdings, global pnl, value curve, etc) in raw sql queries.
  \item hands on experience with high demand infra.
  \item \textbf{Technologies Used:} Golang, Python, Postgresql, mongodb, redis, AWS, Docker.
  \vspace{3pt}
  \end{resume_list}


  \begin{resume_list}
  \itemTitle{School Of Stocks (Edtech Platform)}
  \item Worked on an educational technology platform focused on stock market training for the FinTech company Fyers.
  \item Responsible for developing the entire backend using the Python-based Django framework.
  \item Integrated the project with OpenEDX, an open-source learning platform also built with Django.
  \item \textbf{Technologies Used:} Python, Django, OOP, Postgresql, mongodb, redis, AWS, Docker.
  \vspace{3pt}
  \end{resume_list}


\headingBf{Menkou (Full Time - Remote)}{2020-Aug 2022}
\headingIt{Backend Engineer}

    \begin{resume_list}
    \item Worked as full stack developer in Django Python, NodeJS
    \item worked with javascript, creating frontend pages.
    \item worked with data scraping automation in python
    \item \textbf{Technologies Used:} Nodejs, Python, mysql, Pandas, numpy, selenium, bs4, bigquery.
    \vspace{3pt}
    \end{resume_list}

\section{Open Source Project}
\begin{resume_list}
\item building a open-source notifier service(golang) which anyone can use
\item this serivce is suppose to be supporting multiple channels of notification
\item Making it flexible enough to plug new channels
\end{resume_list}

\end{document}
